Luminance constancy under fixed geometry

### 2018-05-02 Draft4/draft4.tex
small edits
Today’s edits in discussion.

Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition. 
In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy problem and performance is essentially perfect for both the baseline linear regression and AMA methods.
In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
Indeed, neither of our methods performs well when they directly process the cone isomerizations.
Performance with both methods improves greatly when the cone isomerizations are contrast normalized. 
Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
Linear regression does less well, in part because it only has access to cone isomerizations at image locations
corresponding to the target object.
In addition, AMA makes optimal use of the stimulus information across a wider range
of conditions than linear regression.
Condition 2, however, does not include scene to scene variation in the background surface reflectances
as occurs in natural viewing.
The results for Condition 3 show performance when we add such variation.
Performance here represents the overall level of luminance constancy that our methods achieve for the
most realistic condition that we tested.
In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.

@@

\subsection{Importance of Background Variation}

@@

\subsection{Limitations Future Directions}
Geometric variations
Material and texture variation
Other dimensions of color space

\subsection{Linking to Human Performance}
Constancy indices
Weber fractions
Experiments with virtual scenes

The variability in the final condition results from changes in background object spectra, which affects the estimation in two ways.
First, it affects the estimation of cone contrast due to the variability in the background.
Second, it also effects the cone isomerizations corresponding to the target object through 
variability in secondary reflections from the background objects.
While the first effect can be minimized by a representative sampling of the background, 
the effect of secondary reflections can not be removed through simple manipulations.
This effect has largely been ignored in the field. 
We show that such effects are significant.

The reason such effects have been ignored is that we have lacked tools to quantify their effects.
In this regard, a major contribution of this work is the development of a computational package to
produce naturalistic images with precise control over factors defining the scene.
With this software we can systematically vary these factors and precisely quantify their effects on constancy.

>>>>

@@

Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition. 
In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy problem and performance is essentially perfect for both the baseline linear regression and AMA methods.
In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
Indeed, neither of our methods performs well when they directly process the cone isomerizations.
Performance with both methods improves greatly when the cone isomerizations are contrast normalized. 
Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
Linear regression does less well, in part because it only has access to cone isomerizations at image locations
corresponding to the target object.
In addition, AMA makes optimal use of the stimulus information across a wider range
of conditions than linear regression.
Condition 2, however, does not include scene to scene variation in the background surface reflectances
as occurs in natural viewing.
The results for Condition 3 show performance when we add such variation.
Performance here represents the overall level of luminance constancy that our methods achieve for the
most realistic condition that we tested.
In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
Note that introduction of variation in the background surfaces makes the luminance constancy problem substantially harder,
because variation in the background surfaces reduces the reliability of the light reflected from these
surfaces.
%% READ THIS PART

%\subsection{Importance of Background Variation}
%
%
%The variability in the final condition results from changes in background object spectra, which affects the estimation in two ways.
%First, it affects the estimation of cone contrast due to the variability in the background.
%Second, it also effects the cone isomerizations corresponding to the target object through 
%variability in secondary reflections from the background objects.
%While the first effect can be minimized by a representative sampling of the background, 
%the effect of secondary reflections can not be removed through simple manipulations.
%This effect has largely been ignored in the field. 
%Our work shows that such effects are significant.
%
%The reason such effects have been ignored is that we have lacked tools to quantify their effects.
%In this regard, a major contribution of this work is the development of a computational package to
%produce naturalistic images with precise control over factors defining the scene.
%With this software we can systematically vary these factors and precisely quantify their effects on constancy.

@@

\subsection{Future Directions}

In the work presented here, we incorporated spectral variation into our statistical model
of naturalistic scenes.
It is natural to begin with spectral variation, because this variation is at the heart of
what makes luminance constancy a rich computational problem.
In natural scenes, however, there are other sources of variation that add additional
richness.
These include variation in non-spectral properties of objects and lighting in the scene, including
object texture, material, and shape as well as lighting geometry.
The methods we developed here may be generalized to study the effects of variation
in these factors.
The basic approach would be to incorporate the variation into the generation of the
scenes and again learn estimators from the corresponding labeled images.
A challenge for this approach will be to thoughtfully control the increase in problem
complexity both to keep compute time feasible and to ensure that it is possible to
extract meaningful insight from the results.

Luminance constancy is a special case of the more general problem of color constancy.
The approach we developed here could easily be generalized to the estimation of additional
surface reflectance descriptors, such as object hue or chroma.
As with LRV these descriptors would be defined by the light reflected from an object 
under a standard illuminant.
A further advance would be to develop methods for learning receptive fields that are
optimal for multivariate estimation problems.
With such methods one could directly estimate three-dimensional color descriptors.

\subsection{Linking to Human Performance}

An important motivation for studying the computational problem of luminance constancy
is to gain insight about human vision.
The approach we developed can be used to make predictions of how humans would
perform in a psychophysical task that probes the visual representation of object LRV.
For example, one could study discrimination thresholds for target LRV using the
stimuli that were generated with the methods used
here.
For example, we could ask how LRV discrimination thresholds are impacted by 
spectral variation in the illuminant, the background objects, and in the target object itself.
Comparing human thresholds with the precision of AMA-based estimates would then
allow inferences about how well human observers make use of the information available
in the images for performing the LRV discrimination task.
We think experiments and analyses along these lines represent an important future direction.
By coupling the experiments and analyses, we hope to advance our understanding
of how we see objects in the real world in a principled and controlled manner.
